% Chapter 1

\chapter{Introduction} % Chapter title

\label{ch:introduction} % For referencing the chapter elsewhere, use \autoref{ch:introduction}

%----------------------------------------------------------------------------------------

Aircraft systems record large quantities of data during flight. A lot of this data is necessary in the system 's proper functioning. It takes an even more significant role when investigating air accidents.
As this data establishes the causes behind those accidents, it aids measures to prevent such accidents from occurring. That is the primary reason for why recovery of Flight Data Recorders \footnote{Popularly referred to as `Blackboxes`} is usually a very high priority for aircraft investigations.\\

The data itself features many components tracked over time, including but not limited to the following\footnote{The following components were part of the sample dataset I was given for testing.}:
\begin{itemize}
\item Latitude
\item Longtitude
\item Altitude
\item Heading
\item Pitch
\item Roll
\item Engine Thrust
\item Throttle Lever Position
\end{itemize}

As is probably evident, analyzing this largely numeric data by itself would be a painstaking task. Primarily because finding patterns in numbers through observation is inherently difficult. Also because the data set is of a substantially large size \footnote{I will be cautious before calling it ``Big Data''. }. \\

Therefore the need for a tool to visualise this data becomes immediately obvious. \\

The Air Accident Investigation Board (AAIB), a branch of Singapore's Ministry of Transport performs analysis on such flight data, and requested an application that would render relevant flight data quickly and in a portable manner. \\

\section{System Requirements}

AAIB needed the application to meet certain criterias and contain certain core features. These included:

\begin{enumerate}
  \item \spacedlowsmallcaps{Google Earth} Compatibility. Google Earth is a popular ``virtual globe, map and geographic information program''. It provides detailed 3d projections of Google's satellite images on a spherical globe, overlaid with huge quantities of textual and pictorial data varying from international boundaries to streets. There are many good reasons for this requirement including:
    \begin{itemize}
      \item Cross Platform. It works and is supported on Windows, OSX and Linux \footnote{Atleast the desktop version is supported on all three major Operating Systems.}
      \item Extensible through the Keyhole Markup Language (KML) \footnote{A lot more on this later}
      \item Free\footnote{As in beer, not speech}
      \item AAIB's familiarity with it
      \item Offline use. This is quite important as internet access is not guranteed on accident sites
    \end{itemize}
  \item \spacedlowsmallcaps{CSV}\footnote{Comma Separated Values} based input. The system should be able to use large datasets encoded in CSV.
  \item  The system should display the data in its geographical location as vectors. The visualization should be able to reflect the actual data in an intuitive way. For instance, vectors at each data point should represent roll, heading, engine throttle
  \item Users should be able to select which vectors they want to view.
  \item The data points should be manually adjustable from within google earth. This is particularly relevant for data points near landing strips, where measurement errors may cause an offset in the rendered visualization

\end{enumerate}

\section{Style Options}\label{sec:options}

There are a couple of options for \texttt{classicthesis.sty} that allow for a bit of freedom concerning the layout: \marginpar{\dots or your supervisor might use the margins for some comments of her own while reading.}
\begin{itemize}
\item General:
\begin{itemize}
\item\texttt{drafting}: prints the date and time at the bottom of each page, so you always know which version you are dealing with. Might come in handy not to give your Prof. that old draft.
\end{itemize}

\item Parts and Chapters:
\begin{itemize}
\item\texttt{parts}: if you use Part divisions for your document, you should choose this option. (Cannot be used together with \texttt{nochapters}.)

\item\texttt{nochapters}: allows to use the look-and-feel with classes that do not use chapters, \eg, for articles. Automatically turns off a couple of other options: \texttt{eulerchapternumbers}, \texttt{linedheaders}, \texttt{listsseparated}, and \texttt{parts}.

\item\texttt{linedheaders}: changes the look of the chapter headings a bit by adding a horizontal line above the chapter title. The chapter number will also be moved to the top of the page, above the chapter title.
\end{itemize}

\item Typography:
\begin{itemize}
\item\texttt{eulerchapternumbers}: use figures from Hermann Zapf's Euler math font for the chapter numbers. By default, old style figures from the Palatino font are used.

\item\texttt{beramono}: loads Bera Mono as typewriter font. (Default setting is using the standard CM typewriter font.)
\item\texttt{eulermath}: loads the awesome Euler fonts for math. (Palatino is used as default font.)

\item\texttt{pdfspacing}: makes use of pdftex' letter spacing capabilities via the \texttt{microtype} package.\footnote{Use \texttt{microtype}'s \texttt{DVIoutput} option to generate DVI with pdftex.} This fixes some serious issues regarding math formul\ae\ etc. (\eg, ``\ss'') in headers.

\item\texttt{minionprospacing}: uses the internal \texttt{textssc} command of the \texttt{MinionPro} package for letter spacing. This automatically enables the \texttt{minionpro} option and overrides the \texttt{pdfspacing} option.
\end{itemize}

\item Table of Contents:
\begin{itemize}
\item\texttt{tocaligned}: aligns the whole table of contents on the left side. Some people like that, some don't.

\item\texttt{dottedtoc}: sets pagenumbers flushed right in the table of contents.

\item\texttt{manychapters}: if you need more than nine chapters for your document, you might not be happy with the spacing between the chapter number and the chapter title in the Table of Contents. This option allows for additional space in this context. However, it does not look as ``perfect'' if you use \verb|\parts| for structuring your document.
\end{itemize}

\item Floats:
\begin{itemize}
\item\texttt{listings}: loads the \texttt{listings} package (if not already done) and configures the List of Listings accordingly.

\item\texttt{floatperchapter}: activates numbering per chapter for all floats such as figures, tables, and listings (if used).

\item\texttt{subfig}(\texttt{ure}): is passed to the \texttt{tocloft} package to enable compatibility with the \texttt{subfig}(\texttt{ure}) package. Use this option if you want use classicthesis with the \texttt{subfig} package.

\end{itemize}

\end{itemize}

\noindent The best way to figure these options out is to try the different possibilities and see, what you and your supervisor like best.

In order to make things easier in general, \texttt{classicthesis-config.tex} contains some useful commands that might help you.

%----------------------------------------------------------------------------------------

\section{Customization}\label{sec:custom}

This section will give you some hints about how to adapt \texttt{classicthesis} to your needs.

The file \texttt{classicthesis.sty} contains the core functionality of the style and in most cases will be left intact, whereas the file \texttt{classic\-thesis-config.tex} is used for some common user customizations.

The first customization you are about to make is to alter the document title, author name, and other thesis details. In order to do this, replace the data in the following lines of \texttt{classicthesis-config.tex:}\marginpar{Modifications in \texttt{classic\-thesis-config.tex}
}

\begin{lstlisting}[frame=lt]
\newcommand{\myTitle}{A Classic Thesis Style\xspace}
\newcommand{\mySubtitle}{An Homage to ...\xspace}
\newcommand{\myDegree}{Doktor-Ingenieur (Dr.-Ing.)\xspace}
\end{lstlisting}

Further customization can be made in \texttt{classicthesis-config.tex} by choosing the options to \texttt{classicthesis.sty} (see~\autoref{sec:options}) in a line that looks like this:

\begin{lstlisting}[frame=lt]
\PassOptionsToPackage{eulerchapternumbers,listings,drafting, pdfspacing, subfig,beramono,eulermath,parts}{classicthesis}

\end{lstlisting}

If you want to use backreferences from your citations to the pages they were cited on, change the following line from:
\begin{lstlisting}[breaklines=false,frame=lt]
\setboolean{enable-backrefs}{false}
\end{lstlisting}
to
\begin{lstlisting}[breaklines=false,frame=lt]
\setboolean{enable-backrefs}{true}
\end{lstlisting}

Many other customizations in \texttt{classicthesis-config.tex} are possible, but you should be careful making changes there, since some changes could cause errors.

Finally, changes can be made in the file \texttt{classicthesis.sty}, \marginpar{Modifications in \texttt{classicthesis.sty}} although this is mostly not designed for user customization. The main change that might be made here is the text-block size, for example, to get longer lines of text.

%----------------------------------------------------------------------------------------

\section{Issues}\label{sec:issues}
This section will list some information about problems using \texttt{classic\-thesis} in general or using it with other packages.

Beta versions of \texttt{classicthesis} can be found at the following Google code repository:
\begin{center}
\url{http://code.google.com/p/classicthesis/}
\end{center}

\noindent There, you can also post serious bugs and problems you encounter.

\subsection*{Compatibility with the \texttt{glossaries} Package}
If you want to use the \texttt{glossaries} package, take care of loading it with the following options:
\begin{verbatim}
\usepackage[style=long,nolist]{glossaries}
\end{verbatim}

\noindent Thanks to Sven Staehs for this information.

\subsection*{Compatibility with the (Spanish) \texttt{babel} Package}
Spanish languages need an extra option in order to work with this template:
\begin{verbatim}
\usepackage[spanish,es-lcroman]{babel}
\end{verbatim}

\noindent Thanks to an unknown person for this information (via Google Code issue reporting).

\subsection*{Compatibility with the \texttt{pdfsync} Package}
Using the \texttt{pdfsync} package leads to linebreaking problems with the \texttt{graffito} command. Thanks to Henrik Schumacher for this information.

%----------------------------------------------------------------------------------------

\section{Future Work}
So far, this is a quite stable version that served a couple of people well during their thesis time. However, some things are still not as they should be. Proper documentation in the standard format is still missing. In the long run, the style should probably be published separately, with the template bundle being only an application of the style. Alas, there is no time for that at the moment\dots it could be a nice task for a small group of \LaTeX nicians.

Please do not send me email with questions concerning \LaTeX\ or the template, as I do not have time for an answer. But if you have comments, suggestions, or improvements for the style or the template in general, do not hesitate to write them on that postcard of yours.

%----------------------------------------------------------------------------------------

\section{License}
\paragraph{GNU General Public License:} This program is free software; you can redistribute it and/or modify it under the terms of the \textsmaller{GNU} General Public License as published by the Free Software Foundation; either version 2 of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful, but \emph{without any warranty}; without even the implied warranty of \emph{merchantability} or \emph{fitness for a particular purpose}. See the \textsmaller{GNU} General Public License for more details.
